\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates on progress

For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number. If \textit{Ca} is too high \citet{saffman_1959}, \citet{homsy_1987}, \citet{tabeling_1987} and other agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity U.

>>>>

For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number. If \textit{$N_{c}$} is too high \citet{saffman_1959}, \citet{homsy_1987}, \citet{tabeling_1987} and other agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity U.
